A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-24 manuscript/manuscript.tex
fixed typos in manuscript and response

Node inputs and ouputs are connected to each other, and to inputs and outputs of the pipeline, by
providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
arguments take a dictionary. The keys of the \emph{inputs} dictionary correspond to
trait names in the node's input specification, whereas the keys of the \emph{outputs} dictionary correspond to
names of entries in the study data specification. The values of both dictionaries are 2-tuples. For pipeline
inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the study data specification
and the format the input data is expected in (i.e. a FileFormat for Fileset specifications or core Python type for Field specifications).
For pipeline outputs, values of the \emph{outputs} dictionary consist of a trait name in the node's output specification and the format the
output data is generated in. For input connections from other nodes, values of the \emph{inputs} dictionary
consist of a reference to the upstream node and the name of a trait in the
upstream node's output specification (output connections to other nodes are implied by input connections to the receiving nodes).

>>>>

Node inputs and outputs are connected to each other, and to inputs and outputs of the pipeline, by
providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
arguments take a dictionary. The keys of the \emph{inputs} dictionary correspond to
trait names in the node's input specification, whereas the keys of the \emph{outputs} dictionary correspond to
names of entries in the study data specification. The values of both dictionaries are 2-tuples. For pipeline
inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the study data specification
and the format the input data is expected in (i.e. a FileFormat for Fileset specifications or core Python type for Field specifications).
For pipeline outputs, values of the \emph{outputs} dictionary consist of a trait name in the node's output specification and the format the
output data is generated in. For input connections from other nodes, values of the \emph{inputs} dictionary
consist of a reference to the upstream node and the name of a trait in the
upstream node's output specification (output connections to other nodes are implied by input connections to the receiving nodes).
